---
title: "Lab 01 - Hello R"
author: "Zi Li"
date: "1/22"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

# Load packages and data

```{r load-packages, message=FALSE}
install.packages("tidyverse")
install.packages("datasauRus")
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```
  
# answer for Ex 1: we have 13 rows and 2 columns. we have these variables: away, bullseye, circle, dino, dots, h_lines, high_lines, slant_down, slant_up, star, v_lines, wide_lines, x_shape.  

### Exercise 2

# First, let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

# calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
Once you’ve cleaned up the text, add your own explanation or observations here!
# answer for Ex.2: we filter the dataset "dino" and plot it out, it's a dinosaurs. and we run the correlation anaysis between our X-asix and Y-asix, it's -0.06, not a super strong negative correlation. 

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

dino_data %>%
  summarize(r = cor(x, y))
```

# the r=-0.06, not a strong correlation tho. 

# explanation: the correaltion here is the same, which make sense, cause it's the same dataset, we just plot it into different shape. 


### Exercise 4

```{r plot & cor for circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

circle_data %>%
  summarize(r = cor(x, y))
```

# compare with Ex 3. the r for Ex. 4 increase a bit, now it's -0.068, still not a strong correlation. 
# I'd like to change my explanation I made for Ex.3, they are not the same dataset, the command "filter" already select the data form the whole dataset. 

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


